Appendix S1 - _Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models_

### 2020-12-01 analysis/paper/appendix/appendix_s1.Rmd
updated the appendix to keep a copy of the .tex file. Replaced the formatting of author names in that .tex file (to avoid overrunning a line), and re-compiled the pdf

---
title: "Appendix S1"
subtitle: "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@merck.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      number_sections: FALSE
      geometry: margin=1in
      latex_engine: "xelatex"
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks2.lua
      - --lua-filter=../../templates/pagebreak.lua
      includes:
        in_header: ../../templates/header_appendixS.tex
    bookdown::word_document2:
      fig_caption: yes
      toc: no
      always_allow_html: true
      number_sections: FALSE
      fig_height: 7
      fig_width: 6
      reference_docx: "../../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- ../references.bib
- ../packages.bib
csl: "../../templates/ecological-applications.csl" # Insert path for the bib-style
---

>>>>

---
title: Appendix S1 - _Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models_
subtitle: "Ecospheres"
author:
- Kevin E. See:
    email: Kevin.See@merck.com
    institute: [biomark]
    correspondence: true
- Michael W. Ackerman:
    email: Mike.Ackerman@merck.com
    institute: [biomark]
    correspondence: false
- Richard A. Carmichael:
    email: Richard.Carmichael@merck.com
    institute: [biomark]
    correspondence: false
- Sarah L. Hoffmann:
    email: Sarah.Hoffmann@merck.com
    institute: [biomark]
    correspondence: false
- Chris Beasley:
    email: Chris.Beasley@merck.com
    institute: [biomark]
    correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      number_sections: FALSE
      geometry: margin=1in
      latex_engine: "xelatex"
      keep_tex: true
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks2.lua
      - --lua-filter=../../templates/pagebreak.lua
      includes:
        in_header: ../../templates/header_appendixS.tex
    bookdown::word_document2:
      fig_caption: yes
      toc: no
      always_allow_html: true
      number_sections: FALSE
      fig_height: 7
      fig_width: 6
      reference_docx: "../../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- ../references.bib
- ../packages.bib
csl: "../../templates/ecological-applications.csl" # Insert path for the bib-style
---
